Case for Support

### 2021-11-14 communityDemand.tex
Added reference to focus on neuro applications

That there is a need for an easier interface into machine learning algorithms
is evidenced by the development of multiple graphical user interfaces for
tracking animal behaviour over the last several years, especially in the much
larger Python user community
\citep[e.g.,][]{walterAndCouzin21,guilbeaultEtAl21}. However, these graphical
user interfaces have no interact with real-time experimental control, and
their support libraries require expertise with the Python programming language
to use flexibly. Bonsai provides a way of addressing this gap, using its
flexible visual programming language to combine ease-of-use and full
flexibility for experimental control.

>>>>

That there is a need for an easier interface into machine learning algorithms
is evidenced by the development of multiple graphical user interfaces for
tracking animal behaviour over the last several years, especially in the much
larger Python user community
\citep[e.g.,][]{walterAndCouzin21,guilbeaultEtAl21}. However, these graphical
user interfaces have no interaction with real-time experimental control, and
their support libraries require expertise with the Python programming language
to use flexibly. Bonsai provides a way of addressing this gap, using its
flexible visual programming language to combine ease-of-use and full
flexibility for experimental control.

We focused this proposal on neuroscience applications of Bonsai. However, the
addition of machine intelligence functionality is needed in many other
experimental areas where Bonsai is or could be used. Therefore, the software
abstractions that we will build to add to Bonsai machine intelligence
functionality for neuroscience experiments (e.g., methods to perform
multi-method comparisons) will translate to other application domains of
Bonsai.
